Understanding the Data Duplication in VM Cloud Storage

### 2012-05-06 data_analysis/cds.tex
camera ready pdf

We let $M$ be the number of machines in a VM cluster, $N$ be the total number of VMs,
$D$ denotes the average size of one VM's snapshot backups, which is near 40 GB in our production clusters.
And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in CDS,
then the total size of CDS is represented by $C=C_0+C_s+C_u$.
We let $S_0$, $S_s$ and $S_u$ denote the corresponding average space saving ratio (coverage) relative to $D$ in per VM's snapshot backups,
so the total saving ratio is $S=S_0+S_s+S_u$.

>>>>

We let $M$ be the number of nodes in a cluster, $N$ be the number of VMs hosted per node,
and let $D$ denotes the average size of one VM's snapshot backups (after level 1 and 2 reduction, which is near 40 GB in our production environment).
And let $C_0$, $C_s$ and $C_u$ denote the size of zero-filled block, system-related data and user-generated data in CDS,
then the total size of CDS is represented by $C=C_0+C_s+C_u$.
We let $S_0$, $S_s$ and $S_u$ denote the corresponding data coverage ratio (with respect to $D$) by $C_0$, $C_s$ and $C_u$,
so the total space saving ratio is $S=S_0+S_s+S_u$.
